\begin{problem}
  Suppose $\equiv$ is an equivalence relation on $C$ with finitely many
  equivalence classes. Describe all the complete (consistent) theories
  of $T$ with the property that $Cn \Sigma_\equiv \subset T$, by saying
  what sentences you need to add to $\Sigma_\equiv$ to produce the set
  of axioms for $T$.

  \emph{Hint: } Consider the possible ways to get finite or infinite
  countable models of $Cn \Sigma_\equiv$ that are not isomorphic.
  Then consider whether these non-isomorphic structures have
  different theories.

  Since every complete theory of $\cL$ contains some $Cn \Sigma_\equiv$
  (because every structure for $\fL$ satisfies some $\Sigma_\equiv$),
  problems (4) and (5) together describe all the complete theories of $\cL$.

\end{problem}
\begin{Answer}
  First, $T$ must satisfy all the consequences of $\Sigma_\equiv$, i.e.
  $Cn \Sigma_\equiv \subset T$, so the set of axioms of $T$ must contain all
  the axioms in $\Sigma_\equiv$.
  
  One way to generate axioms for $T$ is by adding axioms to $\Sigma_\equiv$
  that specify additional elements but do not alter the conditions that
  $\Sigma_\equiv$ places on the constant symbols.

  \step
  For example:

  \begin{enumroman}
    \item $\Sigma_1 = \Sigma_\equiv \cup
      \set{ \exists x_1 \forall c_i^\fA \lnot (x_1 = c_i^\fA) }$
      specifies that $\abs{\fA}$ contains translations of
      all the constant symbols and $\abs{\fA}$ also contains
      at least one non-constant symbol.
    \item $\Sigma_2 = \Sigma_1 \cup \set{
      \exists x_1 \exists x_2 ( \lnot (x_1 = x_2) \land
      \forall c_i (\lnot (x_1 = c_i) \land \lnot (x_2 = c_i)))}$
      specifies that $\fA$ contains translation of the constant symbols
      and it also contains at least two non-constant symbols.
    \item Inductively, we define $\Sigma_n$ as follows:
      \begin{align*}
        \Sigma_n &= \Sigma_{n-1} \cup \set{
          \exists x_1 \ldots \exists x_n
          ( \lnot (x_1 = x_2) \land \ldots \land \lnot (x_{n-1} = x_n) \land
          \forall c_i (\lnot (x_1 = c_i) \land \ldots \land
          \lnot (x_n = c_i)))}
      \end{align*}
      
      Define $x_n$ to be the new non-constant symbol
      added at step $n$, then $\Sigma_n$ is countable.
      It is also finite for all finite $n$.
  \end{enumroman}
  $\Sigma_1$ and $\Sigma_2$ are not isomorphic since they have different
    cardinalities. Likewise, all such finite models of $\fA$ 
    that have different cardinalities are not isomorphic and they
    have different theories.


\end{Answer}
