\begin{problem}
  We define the difference of two sets $X$ and $Y$,
  written $X - Y$, to be the set of all members of $X$
  that are not members of $Y$.
  Suppose $X$ is an effectively enumerable set of expressions
  and $Y$ is a decidable set of expressions.
  \begin{enumalph}
    \item Show that $X - Y$ is effectively enumerable.
      \begin{Answer}
        Since $X$ is effectively enumerable, we can write a program to list
        all the elements of $X$, although the program may never halt.
        On the other hand, $Y$ is decidable, so given any wff $\alpha$,
        we can determine whether $\alpha$ is a member of $Y$.

        \step
        To determine the members of $X - Y$, we can proceed as follows:
        \begin{enumroman}
          \item Start the algorithm to list members of $X$.
          \item Each moment a member is listed, check whether the listed wff
             is a member of $Y$ (since $Y$ is decidable).
            \begin{itemize}
              \item If it is a member of $Y$, discard the wff.
              \item If it is not a member of $Y$, list it as a member of $X - Y$.
            \end{itemize}
          \item Repeat from step (i).
        \end{enumroman}
        Since all members of $X - Y$ are members of $X$,
        every such wff will be listed as a member of $X$,
        therefore $X - Y$ is effectively enumerable.
      \end{Answer}
    \newpage
    \item Suppose that $X$ is not decidable, and $X \subseteq Y$,
      show that $Y - X$ is not effectively enumerable.
      \begin{Answer}
        Since all decidable sets are effectively enumerable,
        we can effectively list all the members of $Y$,
        although an program to do so may never halt.

        \step
        We could have proceeded as above,
        only swapping the roles of $X$ and $Y$.
        However, to determine that a member of $Y$ is a member of $Y - X$,
        we must determine that they are not a member of $X$,
        and $X$ is not decidable so we cannot do so.
        Therefore, even though we can list members of $Y$,
        we cannot determine the membership of all such members in $Y - X$,
        so $Y - X$ is not effectively enumerable.

        \step
        Note: the fact that both $X$ and $Y$ are effectively enumerable
        does not help us in this case.
        To effectively list all the members of $Y - X$,
        we would have to somehow list all the members of $Y$,
        list all the members of $X$, then compare the two.
        However, the programs to list all the members of $Y$ and $X$
        are not guaranteed to halt, so we cannot compare the two.

      \end{Answer}
  \end{enumalph}
\end{problem}
