\begin{problem}
  This is a problem in first order logic.

  \step
  It is also a short answer problem.
  That is, giving a correct answer is sufficient;
  no explanation is needed.

  \step
  Feel free to use the following abbreviations and conventions:
  You may use any of our five sentential logic connectives,
  write $=, <, +, -$ using infix notation
  (e.g. $x = y$ instead of $= xy$), use the quantifier $\exists$,
  call your variables $x$ and $y$ (or even $\delta$ and $\eps$),
  and omit parenthesis, include extra parentheses,
  and use other kinds or sizes of parentheses
  (such as $[ ]$ and ${}$) to enhance readability.
  However, ``$(\forall \eps > 0)$,'' ``$\le$,'' and ``$\ne$'',
  for example, are not abbreviations we have defined.
  You may, however, define your own abbreviations.
  For example, you may say something like:
  ``for any terms $t_1$ and $t_2$, let $t_1 > t_2$ be an abbreviation
  for the formula $t_2 < t_1$.
  If you do this, be careful to be technically correct.
  For example, do not say
  ``Let $\le$ be an abbreviation for $< \lor =$''.
  
  \step
  Let $\frakL$ be the language for first order logic that has equality,
  constant symbols $0$ and $r$, one-place function symbols $f$ and $a$,
  two-place function symbols $+$, $-$, and $\cdot$,
  and a two-place predicate symbol $<$.
  Translate the parameters of this language as follows.
  Note: ``Translate $r$ as a real number''
  means that $r$ is the name of some specific real number,
  we just aren’t saying which one; similarly for
  ``translate $f$ as a function.''

  \begin{table}[H]
    \begin{tabular}{|l|l|}
      \bottomrule
      \textbf{Symbol} & \textbf{Translation} \\
      \midrule
      $\forall$ & for all real numbers \\
      $0$ & zero \\
      $r$ & a real number \\
      $f$ & a function from $\R$ to $\R$ \\
      $a$ & the absolute value function \\
      $+$ & addition \\
      $-$ & subtraction \\
      $\cdot$ & multiplication \\
      $<$ & less than \\
      \toprule
    \end{tabular}
    \caption{Translation of symbols}
  \end{table}

  \step
  \begin{enumalph}
    \item Write down sentences that mean:
      \begin{enumroman}
        \item The function $f$ is strictly increasing.
        \begin{Answer}
          \[ \forall x \forall y (\; (x < y) \lto (f(x) < f(y))\;) \]
        \end{Answer}
        \item Every square is the absolute value of some number.
        \begin{Answer}
          \step
          For any $x$, we define $x^2$ to be an abbreviation for $x \cdot x$.

          \step
          For any $x, y$, we define 

          \[ \forall x \; ( \exists y (\lnot (((x^2 - ay) < 0) \lor ((ay - x^2) < 0)))) \]
        \end{Answer}
      \end{enumroman}
    \item Translate the following sentences into English:
      \begin{enumroman}
        \item $\forall x \forall y (= fx\ fy \lto = x y)$
          \begin{Answer}
            If $f$ maps any two real numbers $x$ and $y$
            to the same real number,
            then $x$ and $y$ are equal.
          \end{Answer}
        \item $(\lnot \forall y (\lnot = fy\ r))$
          \begin{Answer}
            There is some real number $y$ such that $f$ maps $y$ to $r$.
          \end{Answer}
      \end{enumroman}
    \item Write down the sentence of $\frakL$ meaning
    \item ``$f$ is not continuous at $r$.''
      \begin{Answer}
        \[ \exists \eps \forall \delta \; ( \crim{((0 < \eps) \land (0 < \delta))} \lto (\crim{(\eps < (a\; f\; (x - \delta)))} \lor \crim{(\eps < (a\; f\; (x - \delta)))})) \]
      \end{Answer}
  \end{enumalph}
\end{problem}
